Who does big team science?

### 2023-03-15 manuscript_scopus.Rmd
you get a doc!

keywords          : "big team, science, authorship, credit"
wordcount         : "X"
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
#documentclass     : "apa6"
classoption       : "man"
#output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib

@@

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja'`)"
documentclass     : "apa7"
output            : papaja::apa6_docx
---

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
```

>>>>

keywords          : "big team, science, authorship, credit"
wordcount         : "X"
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
classoption       : "man"
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib

@@

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_docx
---

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
```
